Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-02 documentation/paper.tex
Removed specific mention of iterative cluster nucleation

The objective of this study is to solve all 3 of these problems using machine learning. This is done with a semi-supervised algorithm called \textit{iterative cluster nucleation}, which simultaneously learns an effective discriminator and improves the purity of its own training data set.

@@

Since iterative cluster nucleation incorporates a neural network model, optimization is a much simpler task if the network's hyperparameters are already optimized. Thus, the optimization task is split into two distinct phases:

\begin{enumerate}
    \item Optimize the hyperparameters of a neural network on validation accuracy, to accurately reproduce the imperfect ground truths it is trained on. While this does not produce an optimal discriminator, it does reveal architectures that are capable, in essence, of learning to accomplish the discrimination task.
    \item Using neural network hyperparameters that were determined to be effective, optimize the hyperparameters of the iterative cluster nucleation algorithm to reproduce Acoustic Parameter as closely as possible. Since Acoustic Parameter is not used to optimize the neural network directly at any point, models that excel at this task demonstrate an ability to learn the desired discriminator while ignoring the impurities in the training set.
\end{enumerate}

@@

@@

>>>>

The objective of this study is to solve all 3 of these problems using machine learning. This is done using semi-supervised algorithms that simultaneously learn an effective discriminator and improves the purity of its own training data set.

@@

Since the semi-supervised learning algorithms used incorporate  neural network models, optimization is a much simpler task if the network's hyperparameters are already optimized. Thus, the optimization task is split into two distinct phases:

\begin{enumerate}
    \item Optimize the hyperparameters of a neural network on validation accuracy, to accurately reproduce the imperfect ground truths it is trained on. While this does not produce an optimal discriminator, it does reveal architectures that are capable, in essence, of learning to accomplish the discrimination task.
    \item Using neural network hyperparameters that were determined to be effective, optimize the hyperparameters of the semi-supervised learning algorithm to reproduce Acoustic Parameter as closely as possible. Since Acoustic Parameter is not used to optimize the neural network directly at any point, models that excel at this task demonstrate an ability to learn the desired discriminator while ignoring the impurities in the training set.
\end{enumerate}

@@

\subsection{For Supervised Learning}

@@

\subsection{For Semi-Supervised Learning}

Semi-supervised learning algorithms were scored based on how well they were able to learn to reproduce Acoustic Parameter. ADD MORE INFORMATION HERE BASED ON HOW ANALYSIS IS DONE.
